---
title: "Initial Korean covid 19"
author: "Kiara Butler "
date: "october 18 "
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?
This is a categorical~categorical comparison that looks at the data of covid in Korea to see if dying is independent of the sex of an individual whether they are male or female. The first variable is Sex which is categorized as "F" and "M" for male and female. The second variable is the results of their condition which are categorized as "alive" and "dead."

Analyzing the data will allow us to see if there is a correlation between the result of dead or alive and the sex of the individual or if both sexes have similar results.

The main hypothesis is that the results of dead and alive are strongly correlated to one sex or the other but, the alternate hypothesis is that the two sexes have similar results of dead and alive.



## Graphical results - use ggplot commands to do this  
```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

This bar graph shows that the female sex has higher results of alive but, the male sex has lower results of being alive and higher results of being dead. This indicates that there is a difference in the results of Covid cases in Korea between the two sexes.
  



  





  
## Numerical results``` {r include = TRUE, echo = FALSE}

``` {r include = TRUE, echo = FALSE}
table2 <- xtabs(~result + sex, data=kRdata)
rowPerc(table2)
colPerc(table2)
```
The table shows that there are higher rates of being alive in the female sex with 98.7% alive and 1.4% dead whereas the male sex has higher rates of death at 3% and 97% alive. 

## Inferential results 

``` {r include = TRUE, echo = FALSE}
chisq.test(table2)
chisqtestGC(table2)
fisher.test(table2)
```
The Chi-squared test and the fisher exact test highlights the disparity between the sexes of male and female in regards to being alive or dead. The p-value of 0.0009 confirms that there is a significant difference in the data with males about 2 times more likely than females to die from covid at least in the case of Korea.



## Conclusions

